Pool Model

### 2023-12-20 pool_model.tex
more comments about code
tell the reader how to get full equations (with lag phase)

@@

>>>>

To obtain the full equations, we additionally need to consider transition between states of lag-phase and growth phase not depicted here.
The preceding equations all assume that cells are in growth phase.
It is however straiforward, to setup these equations.

@@

Since backend of the simulation is written in Rust, so is the implementation of cellular aspects.
Additionally bindings are generated such that the full power of the simulation tool can be accessed.
This significantly improves handling and development time of new models.
